Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-22 latex/main.tex
Add some cites for ARG-like phylo methods

@@

Recombination continues to be treated as a nuisance factor, however~\cite{Neches2020}. 
Overwhelming evidence demonstrates the existance of recombination in SARS-CoV-2
\cite{Jackson2021,VanInsberghe2021,Muller2022bayesian,Focosi2022,Gutierrez2022,Ignatieva2022,Tamura2023},
with multiple deep recombination events now known to be present in 
genealogy of the global population [cites??].
Despite this, phylogenies used as the basis for innumerable studies 
continue to depict the genealogy of SARS-CoV-2 as a single
tree~\cite{McBroome2021,Hadfield2018}.

>>>>

Recombination breaks things\cite{Posada2002effect}

ARG/phylonetwork -like
methods~\cite{Didelot2010inference,Vaughan2017inferring,
Muller2020bayesian,Muller2022bayesian}

Distinction between recombination detection --- identifying that a 
given sequences is a likely recombinant --- and incorporation
of recombination.

Recombination has been incorporated in a number of models

@@

Recombination continues to be treated as a nuisance factor, however~\cite{Neches2020}. 
Overwhelming evidence demonstrates the existance of recombination in SARS-CoV-2
\cite{Jackson2021,VanInsberghe2021,Muller2022bayesian,Focosi2022,
Gutierrez2022,Ignatieva2022,Tamura2023},
with multiple deep recombination events now known to be present in 
genealogy of the global population [cites??].
Despite this, phylogenies used as the basis for innumerable studies 
continue to depict the genealogy of SARS-CoV-2 as a single
tree~\cite{McBroome2021,Hadfield2018}.
